### 2013-07-24 2/literature_review.tex
updated for Ian changes

\chapter{Current Methods in Processing SAR and POLSAR Data} %chapter 2

\section{The Stochastics and Multivariate Nature of POLSAR data}

\subsection{The Stochastic nature of SAR data}

\subsubsection{ Traditional Single-Channel SAR and the Speckle phenomena}

Wikipedia to be edited strongly.
Speckle noise is a granular noise that inherently exists in and degrades the quality of the active radar and synthetic aperture radar (SAR) images.
Speckle noise in conventional radar results from random fluctuations in the return signal from an object that is no bigger than a single image-processing element. It increases the mean grey level of a local area.[1]
Speckle noise in SAR is generally more serious, causing difficulties for image interpretation.[1][2] It is caused by coherent processing of backscattered signals from multiple distributed targets. In SAR oceanography, for example, speckle noise is caused by signals from elementary scatterers, the gravity-capillary ripples, and manifests as a pedestal image, beneath the image of the sea waves.[3][4]

\subsubsection{The Stochastic nature of SAR  and SAR speckle filtering }

The stochastic nature SAR arises from the speckle phenomena.
As SAR speckle seriously hinders the interpretation and understanding of SAR images,
  its effect are routinely reduced through a speckle filtering process.
SAR speckle filtering is the process to suppress the effect of speckle noise SAR images for easier intepretation.

@@

\subsubsection{ Partial Polarimetry and the Stokes Vector}

The dual-polarization modes has been practically and operationally available for quite some time.
However, partial polarimetry has only recently been investigated in the scientific community. 
By comparison, 
	partial polarimetry measures dual-polarized response from incoming pulses of a single polarization channel,
	while full polarimetry measures the same response for two (most of the time orthogonal) polarisation channels.
Mathematically, the process is modelled as:
\begin{equation}
 \left( 
\begin{array}{c}
 E_h^{Rx} \\
 E_v^{Rx}
\end{array}
 \right) = \frac{e^{ikr}}{r} 
\left( 
\begin{array}{c}
 S_{H} \\
 S_{V}
\end{array}
 \right) E^{Tx}
\end{equation}

Souyris \cite{Souyris_2005_TGRS} pioneered the field with his paper on compact polarimetry.
Compact polarimetry is essentially a partial polarimetry mode in which the incoming pulse is of linear polarization, 
	but is neither of the usual horizontal nor vertical angle.
%	rather it is of an odd angle of 
Instead its incoming polarization of linear polarisation with an odd angle of $\pi/4$.
%The $\pi/4$ mode has not been implemented in real-hardware, but only been simulated using polarization basis change principles.
The partial polarimetric covariance matrix then is given as
\begin{equation}
J = 
\left(	
\begin{array}{c c}
	|s_{HH}|^2 + |s_{HV}|^2 + 2 \Re{(s_{HH}s_{HV}^*)}
& 	s_{HH}s_{VV}^* + |s_{HV}|^2 + s_{HH}s_{HV}^* + s_{HV}s_{VV}^*\\
	s_{HH}^*s_{VV} + |s_{HV}|^2 + s_{HV}s_{HH}^* + s_{VV}s_{HV}^*
& 	|s_{VV}|^2 + |s_{HV}|^2 + 2 \Re{(s_{VV}s_{HV}^*)}
\end{array}
\right)
\end{equation}

Raney \cite{Raney_2006_IGARSS} demonstrated a different perspective by proposing a hybrid architecture.
He argued that the dual polarisation measurements effectively capture the polarisation states of the single back-scattered signal resulting from a single incoming pulse.
Thus the polarisation choice of the receiving antenna is trivial (as long as they are orthogonal).
The important parameter to choose is the use of which polarisation for the incoming pulse.
His hybrid architecture is again a kind of partial polarimetry in which the incoming pulse is of circular polarisation, instead of the normally encountered linear polarisation.
The partial covariance matrix then become:
\begin{equation}
J = \frac{1}{2} \left(	
\begin{array}{c c}
	|s_{HH}|^2 + |s_{HV}|^2 + i (s_{HH}s_{HV}^* - s_{HV}s_{VV}^*)
& 	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* - i (|s_{HV}|^2 + s_{HH}s_{VV}^*)\\
	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* + i (|s_{HV}|^2 + s_{HH}s_{VV}^*)
& 	|s_{VV}|^2 + |s_{HV}|^2 + i (s_{HV}s_{VV}^* - s_{VV}s_{HV}^*)
\end{array}
\right)
\end{equation}

The benefits of this hybrid architecture, according to Raney being:
	this partial polarimetric measurements can measures certain physical polarimetric phenomena like odd and even bounce phenomena.
The suggestion is evidenced by calculating the response of known odd-bounce trihedral and even-bounce dihedral when the incident wave is right circular polarized.
\begin{equation}
\Gamma_{tri} = \left(
\begin{array}{c c}
1 & 0 \\
0 & -1
\end{array}
\right)
\end{equation}
Then the response will be reversed as it can be calculated as:
\begin{equation}
J_r = \left(
\begin{array}{c c}
1 & 0 \\
0 & -1
\end{array}
\right) \cdot
\left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) = \left(
\begin{array}{c}
1 \\
i
\end{array}
\right) 
\end{equation}
with
	$ \left( \begin{array}{c} 1 \\ -i \end{array} \right) $ indicating right circular polarization transmitted, and
	$ \left( \begin{array}{c} 1 \\ i \end{array} \right) $ indicating left circular polarization received.

For a dihedral target, whose main axis at an angle $\theta$ with respect to the horizontal direction, the Sinclair matrix is given as:
\begin{equation}
\Gamma_{dih} = 
\left(
\begin{array}{c c}
\cos(2\theta) & \sin(2\theta) \\
\sin(2\theta) & \cos(2\theta)
\end{array}
\right)
\end{equation}
The even bounce phenomena is detectable as its polarimetric response is then:
\begin{equation}
J_r = \left(
\begin{array}{c c}
\cos(2\theta) & \sin(2\theta) \\
\sin(2\theta) & \cos(2\theta)
\end{array}
\right) \cdot
\left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) = \left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) 
\end{equation}
In \cite{Raney_2007_IGARSS}, Raney shows that hybrid circular modes bring many conviniences to hardware calibration.
Also in a follow up study \cite{Raney_2007_TGRS}, he demonstrate the classification power of hybrid polarimetry.
Furthermore, Lardeux \cite{Lardeux_2007_ESASP} found that for target classification using SVM techniques, compact polarimetry mode shows comparable results to full polarimetric data.
Notably, the hybrid architectural concepts has been adopted and brought towards implementation by NASA's upcoming Desdynl satellite \cite{Raney_2009_RadarConf}.

The research into partial polarimetry is convenient as its data can be simulated using polarisation basis transformation described above.
Hardware realisation may not be needed until the final physical prototype stages.
This methodology has been demonstrated and is widely used in the community.
We hypothesize that the partial polarimetric covariance matrix, which is essentially a variant of the Stokes vector, can be speckle filtered, using the familiar intensity speckle filtering algorithms.
The focus into partial polarimetry allow analysis into a smaller matrix, while its implication can be extended not only to full polarimetry modes but also towards bi-static polarimetric scenarios.
Besides that, a number of research questions in this new field are still open, relevant and exciting.

Souyris, in 2005, published a paper \cite{Souyris_2005_TGRS} which claimed and presented an algorithm to reconstruct full polarimetric information from the given partial compact polarimetric data.
The algorithm is claimed to work on natural surfaces.
In \cite{Nord_2009}, Nord reviewed the reconstruction problem for various different partial polarimetry modes, and an improved algorithm is given.
In \cite{Ainsworth_2009_ISPRS}, Ainsworth reviewed performance of target classification on different partial modes, reconstructed pseudo-full mode and full polarimetric data.
Chapter 3 reviews of this sub-topic further and introduces our work on expanding the reconstruction to urban man-made structures and surfaces.

For the tasks of target detection and classification, we believe that partial dual polarization provides a unique offer.
Compared with single-channel, dual channel provide extra polarimetric information. 
Compared with full polarimetric data, the better spatial resolution could makes up for the loss of reconstructed polarimetric information, especially for the purpose of target detection and classification.
\paragraph{ Stokes Vector }

Another way to look at polarization is through the coherency matrix, and equivalently the Stokes matrix.
The wave coherency matrix is defined as:
\begin{equation}
W_c = \left<
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)^{\dagger}
\right>
= \left<
\left(
\begin{array}{c c}
 \xi_x \xi_x^* 	& \xi_x \xi_y^* \\
 \xi_y \xi_x^* 	& \xi_y \xi_y^* 
\end{array}
\right)
\right>
= \left<
\left(
\begin{array}{c c}
 |\xi_x|^2 	& |\xi_x| |\xi_y| e^{-i \Delta \phi} \\
 |\xi_x| |\xi_y| e^{i \Delta \phi} 	& |\xi_y|^2
\end{array}
\right)
\right>
\end{equation}

The Stokes vector is then defined as:
\begin{equation}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_1 \\
 S_2 \\
 S_3
\end{array}
\right)
=
\left(
\begin{array}{c}
 |\xi_x|^2 + |\xi_y|^2 \\
 |\xi_x|^2 - |\xi_y|^2 \\
 2\Re(\xi_x \xi_y^*) \\
 2\Im(\xi_x \xi_y^*)
\end{array}
\right)
\end{equation}

In the case of elementary (or fully polarized) waves, the Stokes vector can be written as:
\begin{equation}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_0 \cos(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\chi)
\end{array}
\right)
\end{equation}

@@

At this point, a distinction needs to be highlighted. %explaination is warranted.
%The naive view is that Stokes vector, which has four values are redundant in describing wave's polarization. 
%In contrary, Stokes vector are preferred to Jones vector, as Jones vector is based on the assumption that the wave is elementary and very well behaved.
In comparison to the two-element Jones vector, Stokes vectors have more data, four elements. 
Jones vector can completely describe the polarization states of an elementary wave, which formulation is based on the assumption that the wave is very well behaved.
In practice, that is not normally the case, because reflected waves are generally combinations of multiple waves which ranged over certain areas of time and frequency. 
As such, the polarization of the waves are normally not fully polarized.
One simple analogy is that the field ratio, i.e. $\xi_x/\xi_y$, or the phase difference, i.e. $\Delta \phi$, are not constant at all times.
The phenomena can be loosely called wave depolarization.

The analysis above is especially prevalent in the remote sensing community, where the area of a single resolution cell (pixel) is very large compared with the radar's wave length.
In such cases, the wave field is very stochastic and only statistical information about the variations and correlations between polarization components can be gathered.

@@

Degree of polarization $p$ is a quantity used to describe the portion of an EM wave, which is polarized.
A perfectly polarized wave has $p=100\%$, while a fully depolarized wave is characterized by $p=0\%$.
A wave which is partially polarized can be represented as a superposition of a polarized and another unpolarized component.
Thus $0 \leq p \leq 1$.

In fully polarized wave, the following equation holds:
\begin{equation}
S_0^2 = S_1^2 + S_2^2 + S_3^2
\end{equation}

In depolarized wave, it becomes an in-equation
\begin{equation}
S_0^2 > S_1^2 + S_2^2 + S_3^2
\end{equation}

Then the degree of polarization is defined as
\begin{equation}
p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}
\end{equation}

In such general case, the Stokes Vector is written as:
\begin{equation}
S_t = 
\left(
\begin{array}{c}
 I \\
 I p \cos(2\Psi) \cos(2\chi) \\
 I p \sin(2\Psi) \cos(2\chi) \\
 I p \sin(2\chi)
\end{array}
\right)
 = I (1 - p)
\left(
\begin{array}{c}
 1 \\
 0 \\
 0 \\
 0
\end{array}
\right) 
+ I p
\left(
\begin{array}{c}
 1\\
 \cos(2\Psi) \cos(2\chi) \\
 \sin(2\Psi) \cos(2\chi) \\
 \sin(2\chi)
\end{array}
\right)
\end{equation}

Or alternatively, if Stokes vector is measured and given, then the polarization characteristics of a wave is given as:
$I$, the total power of the measured beam is $I=S_0$,
$p$, the degree of polarization is calculated as $p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}$,
$2\Psi = \tan^{-1} (S_2/S_1) $ and $2 \chi = \tan^{-1} (S_3 / \sqrt{S_1^2 + S_2^2})$ are the angles that characterize the wave polarization state.

Depolarization phenomena is explained from the fact that most sources of EM radiation contain a large number of ``elementary'' sources.
The polarization of the electric fields produced by the emitters may not be correlated, which leads to depolarization effects.
If there is partial correlation among the ``elementary'' sources, the light is partially polarized. 
One may then describe the received EM wave polarization in terms of the degree of polarization and the parameters of the polarization ellipse.

@@

POLSAR radar measures the back-scattered echo received as the result of transmitting a signal.
The scattering matrix relates the received signal $E^{Rx}$ with the transmitted $E^{Tx}$ signal as:
\begin{equation}
 E^{Rx} = \frac{e^{ikr}}{r} S E^{Tx}
\end{equation}

Normally, horizontal and vertical linear polarization are used, thus the scattering matrix, i.e. $S$, normally have the following expanded form:
\begin{equation}
 \left( 
\begin{array}{c}
 E_h^{Rx} \\
 E_v^{Rx}
\end{array}
 \right) = \frac{e^{ikr}}{r} 
\left( 
\begin{array}{c c}
 S_{HH} & S_{HV} \\
 S_{VH} & S_{VV}
\end{array}
 \right) 
\left( 
\begin{array}{c}
 E_h^{Tx} \\
 E_v^{Tx}
\end{array}
 \right) 
\end{equation}

The scattering matrix can be called the Jones matrix (relating the Jones vector) in the forward scattering alignment.
The matrix is normally called Sinclair matrix in SAR literature, as normally backward scattering alignment are normally used in SAR \cite{Sinclair_1950_ProcsIRE}.
In the case of mono-static SAR, i.e. both radar transmitter and receiver can be considered as located in a single place, physical reciprocity leads to $S_{HV}=S_{VH}$ \cite{Nghiem_1992_RadioSci}.

The matrix can also be "stratified" to define the target scattering vector as: 
\begin{equation}
T_{cv} = \left( 
\begin{array}{c}
 S_{HH} \\
 \sqrt{2} S_{HV} \\
 S_{VV}
\end{array}
 \right) 
\end{equation}
or 
\begin{equation}
T_{ch} = \frac{1}{\sqrt{2}} \left( 
\begin{array}{c}
 S_{HH} + S_{VV}\\
 S_{HH} - S_{VV} \\
 S_{HV}
\end{array}
 \right) 
\end{equation}

>>>>

\chapter{Current Methods in Processing SAR and POLSAR Data} %chapter 2
\label{chap:lit_survey}

This chapter 
reviews the published literature for SAR and POLSAR data processing.
Specifically, its first section describes the multi-dimensional and stochastic nature of the POLSAR data.
The second section then illustrates the different approaches that have been published to address the grand challenge of modelling, processing and ultimately understanding these types of data.

\section{The Stochastic and Multivariate Nature of POLSAR data}

\subsection{The Stochastic Nature of SAR data}

%\subsubsection{ Traditional Single-Channel SAR and the Speckle phenomena}

The stochastic nature of SAR data arises due to the process of SAR image formation. Specifically, since one SAR resolution cell is very big in comparison to the radar wavelength, it normally consists of many elementary scatterers. The data point of each SAR pixel then arises from the combined interference effect of the backscattered waves from these different scatterers. This effect causes natural variation in SAR intensity image even when the underlying scene is highly homogeneous.

SAR speckle phenomena are explained as the interference of many coherent but dephased backscattering components;
  each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. 
The random nature of the SAR data arises
  due to the unknown and varying location, height and thus distance of each elementary scatterer;
  which, in turn, generates random phases in their back-scattering responses.
Assuming the number of these elementary back scatterers is sufficiently large,
  then the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}.
Consequently the interference of these randomly phased responses can be considered as
  a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.  
Specifically the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as
  random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. 
Their probability density functions (PDF) are given as:

\begin{equation}
\label{eqn:SAR Real and Imaginary Components PDF}
\caption{eqn:SAR Real and Imaginary Components PDF}
pdf(A_x)=\frac{1}{\sqrt{\pi} \sigma} e^{\left( \frac{A_x^2}{\sigma^2} \right) }
\end{equation}

It can then be shown that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh distribution.
Subsequently the SAR intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of a negative exponentially distributed random process. The PDFs of these two properties can then be expressed as:

%\begin{eqnarray}
%pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }\\
%pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
%\end{eqnarray}
\begin{equation}
\label{eqn:SAR Amplitude PDF}
\caption{eqn:SAR Amplitude PDF}
pdf(A) = \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }
\end{equation}
\begin{equation}
  \label{eqn:SAR Intensity PDF}
  \caption{eqn:SAR Intensity PDF}
pdf(I) = \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
\end{equation}

%\subsubsection{The Stochastic nature of SAR  and SAR speckle filtering }

%The stochastic nature SAR arises from the speckle phenomena.
As SAR speckle phenomena arises from the stochastic nature of SAR, it seriously hinders the interpretation and understanding of SAR images.
Speckle noise on SAR images are hence routinely reduced through a speckle filtering process for easier human interpretation and more accurate post-processing.
%***IVM: Hai, I added "human" before 'interpretation'. Also added the text afterwards, please check that the sense of the edited text is still correct in terms of what you wanted to say.

@@

\subsubsection{The polarization property of Electro-Magnetic waves}

The propagation of Electro-Magnetic (EM) wave in space is governed by Maxell‚Äôs equations. 
The general solution to these equations is a linear superposition of waves, each having the form of:
\begin{eqnarray*}
 \vec{E}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r}) \\
 \vec{B}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r})
\end{eqnarray*}
where
	$g$ is any well-behaved function of a dimensionless argument $\phi$,
	%for virtually any¬†well-behaved function g¬†of dimensionless argument œÜ, where
	$\omega$ is the angular frequency (in radians per second), and
	$\vec{k}= (k_x,k_y,k_z)$ is the wave vector (in radians per meter).

Because of the divergence between the electric and the magnetic fields, there will be no fields in the direction of wave propagation.
Thus if we define the z direction as the travelling direction of the EM wave,
  then both the electric and the magnetic fields are fluctuating in the x,y plane.
Furthermore, when considering wave propagation, it is conventional that only the electric field vector is described and the magnetic field is ignored since it is perpendicular to the E field and is proportional to it.
Projecting this vector into x,y directions, we have:

\begin{equation*}
\vec{E}(z,t) 
= 
\left(
	\begin{array} {c}
		E_x^0 \cos{ \left( wt - kz  + \phi_x^0 \right) } \\
		E_y^0 \cos{ \left( wt - kz  + \phi_y^0 \right)} \\
		0
	\end{array}
\right)
= 
\left(
	\begin{array} {c}
		\xi_x(t) \\
		\xi_y(t) \\
		0
	\end{array}
\right)
\end{equation*}
where $\phi_0$ is the initial phase angle, that is dependent on the choice of space-time origin.

In other words, the EM vector can oscillate in more than one orientation, and this denote the polarization property of EM wave.
The exact shape traced out in a fixed projective plane by the tip of the electric vector as the plane propagate is a description of the polarization state.
This shape is characterized by the formula: 
\begin{equation*}
 \frac{\xi_x^2(t)}{|E_x^0|^2} + \frac{\xi_y^2(t)}{|E_y^0|^2} - 2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi) = \sin^2(\Delta \phi)
\end{equation*}
where
	$\Delta \phi = \phi_y^0 - \phi_x^0$
The formula characterizes what is termed as the polarization ellipse.

The parameters that describe the polarization ellipse are: 
\begin{equation*}
\tan (\theta ) = \frac{E_y^0}{E_x^0}
\end{equation*}
with
	$0 \leq \theta \leq \pi/2$. 
The orientation angle, which is the angle between the major semi-axis of the ellipse and the x-axis, is given by:
\begin{equation*}
\tan (\Psi) = \tan (2 \theta) \cos(\Delta \phi)
\end{equation*}
with
	$0 \leq \Psi < \pi$. 
The ellipticity, $\epsilon$ is the major-to-minor-axis ratio.
The ellipticity angle which is defined as $\chi = \arctan (1/\epsilon)$ can be calculated as:
\begin{equation*}
\sin (2 \chi) = \sin(2 \theta) \sin( \Delta \phi)
\end{equation*}
with
	$0 \leq \chi \leq \pi/2$, and $0 \leq \epsilon \leq \infty$

Ignoring the scale of the electrical fields, the elementary wave polarization can be completely described by two parameters, i.e. $E_y^0/E_x^0$ and $\Delta \phi = \phi_y^0 - \phi_x^0$. 
Similarly, ignoring the scale of the ellipse, the polarization ellipse can be completely described by two angles $\Psi$ and $\chi$.

Other parameters includes:
\paragraph{ Complex polarization ratio }
This ratio is important in explaining polarization basis changes.

It is defined as:
\begin{equation}
\rho = \frac{E_y^0}{E_x^0} e^{i \Delta \phi} = \frac{\cos(2 \chi) + i \sin(2 \chi)}{1 - \cos(2\Psi) \cos(2\chi)}
\end{equation}

\paragraph{Jones Vector}

%Let the total wave power:
%\begin{equation}
%|E|^2 = (E_x^0)^2  + (E_y^0)^2
%\end{equation}
%and phase 
%\begin{equation}
%\theta = \tan^{-1} \left( \frac{E_y^0}{E_x^0} \right)
%\end{equation}

The Jones vector is defined as 
\begin{equation}
J = 
\left(
\begin{array}{c}
	\xi_x(t) \\
	\xi_y(t) 
\end{array}
\right)
= \xi_x(t)
\left(
\begin{array}{c}
	1 \\
	\rho
\end{array}
\right)
\end{equation}

Thus the normalized Jones vector can be given as:
\begin{equation}
J = 
\left(
\begin{array}{c}
	\cos(\theta) \cdot e^{i \phi_x^0} \\
	\sin(\theta) \cdot e^{i \phi_y^0}
\end{array}
\right)
=
\left(
\begin{array}{c}
	1\\
	\tan(\theta) \cdot e^{i \Delta \phi}
\end{array}
\right)
=
\left(
\begin{array}{c}
	\cos(\Psi) \cos(\chi) - i \sin(\Psi) \sin(\chi) \\
	\sin(\Psi) \cos(\chi) + i \cos(\Psi) \sin(\chi)
\end{array}
\right)
\end{equation}

The two parameters in the Jones vector can completely describe the polarization state (ellipse) of any elementary wave.
This same Jones vector finds extensive use in quantum machenics, and is interpreted as quantum state vector.
Its bra-ket notation formula, which is normally used in quantum computation contexts is:
\begin{equation}
J = | \Psi \rangle 
= 
\left(
\begin{array}{c}
	\cos(\theta) \cdot e^{i \phi_x^0} \\
	\sin(\theta) \cdot e^{i \phi_y^0}
\end{array}
\right)
\end{equation}

By definitions, the horizontal linear polarized wave is defined as: $J_h = \left(
\begin{array}{c}
 1 \\
 0
\end{array}
\right)$, similarly the vertical linear polarized wave: $J_v = \left(
\begin{array}{c}
 0 \\
 1
\end{array}
\right)$, the $\pm \pi/4$ linear polarized waves $J_{\pm} = \pm \frac{1}{\sqrt{2}} \left(
\begin{array}{c}
 1 \\
 1
\end{array}
\right)$, the left circular polarized wave: $J_l = |L\rangle = \frac{1}{\sqrt{2}} \left(
\begin{array}{c}
 1 \\
 -i
\end{array}
\right)$ and the right circular polarized wave: $J_r = |R\rangle = \frac{1}{\sqrt{2}} \left(
\begin{array}{c}
 1 \\
 i
\end{array}
\right)$

\paragraph{ Stokes Vector}

Another way to look at polarization is through the coherency matrix, and equivalently the Stokes matrix.
The wave coherency matrix is defined as:
\begin{equation*}
W_c = \left<
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)^{\dagger}
\right>
= \left<
\left(
\begin{array}{c c}
 \xi_x \xi_x^* 	& \xi_x \xi_y^* \\
 \xi_y \xi_x^* 	& \xi_y \xi_y^* 
\end{array}
\right)
\right>
= \left<
\left(
\begin{array}{c c}
 |\xi_x|^2 	& |\xi_x| |\xi_y| e^{-i \Delta \phi} \\
 |\xi_x| |\xi_y| e^{i \Delta \phi} 	& |\xi_y|^2
\end{array}
\right)
\right>
\end{equation*}

The Stokes vector is then defined as:
\begin{equation*}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_1 \\
 S_2 \\
 S_3
\end{array}
\right)
=
\left(
\begin{array}{c}
 |\xi_x|^2 + |\xi_y|^2 \\
 |\xi_x|^2 - |\xi_y|^2 \\
 2\Re(\xi_x \xi_y^*) \\
 2\Im(\xi_x \xi_y^*)
\end{array}
\right)
\end{equation*}

In the case of elementary (or fully polarized) waves, the Stokes vector can be written as:
\begin{equation*}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_0 \cos(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\chi)
\end{array}
\right)
\end{equation*}

@@

At this point, a distinction needs to be highlighted. %explaination is warranted.
%The naive view is that Stokes vector, which has four values are redundant in describing wave's polarization. 
%In contrary, Stokes vector are preferred to Jones vector, as Jones vector is based on the assumption that the wave is elementary and very well behaved.
In comparison to the two-element Jones vector, Stokes vectors have more data, namely four elements. 
The Jones vector can completely describe the polarization states of an elementary wave, whose formulation is based on the assumption that the wave is very well behaved.
In practice, that is not normally the case, because reflected waves are generally combinations of multiple waves which ranged over certain areas of time and frequency. 
As such, the polarization of the waves are normally not fully polarized.
One simple analogy is that the field ratio, i.e. $\xi_x/\xi_y$, or the phase difference, i.e. $\Delta \phi$, are not constant at all times.
%The phenomena can be loosely called wave depolarization. %****IVM: Hai, is this your term or is it also used by others for the same thing? In that case, it might be good to put a reference here. I think the word "loosely" is one of those trigger words that causes the examiner to sit up and read it critically.

The analysis above is especially prevalent in the remote sensing community, where the area of a single resolution cell (pixel) is very large compared with the radar's wavelength.
In such cases, the wave field is very stochastic and only statistical information about the variations and correlations between polarization components can be gathered.

%(comment: I think it would be better if you can link the two paragraphs together, such as
%ìClosely related to the Stoke vector is the concept of Degree of polarization p, which is a quantity used to describeÖî, or something like this )

@@

Closely related to the Stokes vector is the concenpt of ``Degree of polarization'' $p$, which is a quantity used to describe the portion of an EM wave which is polarized.
A perfectly polarized wave has $p=100\%$, while a fully depolarized wave is characterized by $p=0\%$.
A wave which is partially polarized can be represented as a superposition of a polarized and another unpolarized component.
Thus $0 \leq p \leq 1$.

Depolarization phenomena are explained from the fact that most sources of EM radiation contain a large number of ``elementary'' sources.
The polarization of the electric fields produced by the emitters may not be correlated, which leads to depolarization effects.
If there is partial correlation among the ``elementary'' sources, the light is partially polarized. 
One may then describe the received EM wave polarization in terms of the degree of polarization and the parameters of the polarization ellipse.

In fully polarized wave, the following equation holds:
\begin{equation*}
S_0^2 = S_1^2 + S_2^2 + S_3^2
\end{equation*}

In depolarized wave, it becomes an in-equation
\begin{equation*}
S_0^2 > S_1^2 + S_2^2 + S_3^2
\end{equation*}

Then the degree of polarization is defined as
\begin{equation*}
p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}
\end{equation*}

In such general case, the Stokes Vector is written as:
\begin{align*}
S_t &= 
\left(
\begin{array}{c}
 I \\
 I p \cos(2\Psi) \cos(2\chi) \\
 I p \sin(2\Psi) \cos(2\chi) \\
 I p \sin(2\chi)
\end{array}
\right) \\
 &= I (1 - p)
\left(
\begin{array}{c}
 1 \\
 0 \\
 0 \\
 0
\end{array}
\right) 
+ I p
\left(
\begin{array}{c}
 1\\
 \cos(2\Psi) \cos(2\chi) \\
 \sin(2\Psi) \cos(2\chi) \\
 \sin(2\chi)
\end{array}
\right)
\end{align*}

Alternatively, if the Stokes vector is measured and known, then the polarization characteristics of a wave are given as:
$I$, the total power of the measured beam is $I=S_0$,
$p$, the degree of polarization is calculated as $p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}$,
$2\Psi = \tan^{-1} (S_2/S_1) $ and $2 \chi = \tan^{-1} (S_3 / \sqrt{S_1^2 + S_2^2})$ are the angles that characterize the wave polarization state.

@@

POLSAR radar measures the back-scattered echo received as the result of transmitting a signal.
The scattering matrix relates the received signal $E^{Rx}$ with the transmitted $E^{Tx}$ signal as:
\begin{equation*}
 E^{Rx} = \frac{e^{ikr}}{r} S E^{Tx}
\end{equation*}
%***IVM: Hai, do you need to explain the k & r terms?

Normally, horizontal and vertical linear polarization are used for transmission, and thus the scattering matrix, i.e. $S$, would normally have the following expanded form:
\begin{equation*}
 \left( 
\begin{array}{c}
 E_h^{Rx} \\
 E_v^{Rx}
\end{array}
 \right) = \frac{e^{ikr}}{r} 
\left( 
\begin{array}{c c}
 S_{HH} & S_{HV} \\
 S_{VH} & S_{VV}
\end{array}
 \right) 
\left( 
\begin{array}{c}
 E_h^{Tx} \\
 E_v^{Tx}
\end{array}
 \right) 
\end{equation*}

The scattering matrix can be called the Jones matrix (relating to the Jones vector) in the forward scattering alignment.
The matrix is normally called the Sinclair matrix in SAR literature, as backward scattering alignment is normally adopted for SAR \cite{Sinclair_1950_ProcsIRE}.
In the case of mono-static SAR, i.e. both radar transmitter and receiver can be considered as located in a single place, physical reciprocity leads to $S_{HV}=S_{VH}$ \cite{Nghiem_1992_RadioSci}.

The matrix can also be ``stratified'' to define the target scattering vector as: 
\begin{equation}
  \label{eqn:Covariance Target Vector of Full Polarimetric SAR}
  \caption{eqn:Covariance Target Vector of Full Polarimetric SAR}
T_{cv} = \left( 
\begin{array}{c}
 S_{HH} \\
 \sqrt{2} S_{HV} \\
 S_{VV}
\end{array}
 \right) 
\end{equation}
or 
\begin{equation}
  \label{eqn:Coherence Target Vector of Full Polarimetric SAR}
  \caption{eqn:Coherence Target Vector of Full Polarimetric SAR}
T_{ch} = \frac{1}{\sqrt{2}} \left( 
\begin{array}{c}
 S_{HH} + S_{VV}\\
 S_{HH} - S_{VV} \\
 S_{HV}
\end{array}
 \right) 
\end{equation}

Similar to the reason that Stokes vectors are preferred to Jones vector in wave polarization, 
	second order statistics of the target scattering matrix are normally preferred.
The covariance matrix is defined as:
\begin{equation}
  \label{eqn:Covariance Matrix of Full Polarimetric SAR}
  \caption{eqn:Covariance Matrix of Full Polarimetric SAR}
\tiny{
C_v = \left< T_{cv} T_{cv}^{*T} \right> = 
\left( 
\begin{array}{c c c}
 S_{HH}S_{HH}^* 	& \sqrt{2}S_{HH}S_{HV}^*	& S_{HH}S_{VV}^* \\
 \sqrt{2}S_{HV}S_{HH}^* & 2 S_{HV}S_{HV}^* 		& \sqrt{2}S_{HV}S_{VV}^* \\		
 S_{VV}S_{HH}^*		& \sqrt{2}S_{VV}S_{HV}^*	& S_{VV}S_{VV}^*
\end{array}
 \right) 
}
\end{equation}
while the coherency matrix is defined as:
\begin{equation}
  \label{eqn:Coherence Matrix of Full Polarimetric SAR}
  \caption{eqn:Coherence Matrix of Full Polarimetric SAR}
\tiny{
C_h = \left< T_{ch} T_{ch}^{*T} \right> = \frac{1}{2}
\left( 
\begin{array}{c c c}
 (S_{HH}+S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}+S_{VV})(S_{HH}-S_{VV})^*	& (S_{HH}+S_{VV})S_{HV}^* \\
 (S_{HH}-S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}-S_{VV})(S_{HH}-S_{VV})^* 	& (S_{HH}-S_{VV})S_{HV}^*\\		
 2S_{HV}(S_{HH}+S_{VV})^*		& 2S_{HV}(S_{HH}-S_{VV})^*		& S_{HV}S_{HV}^*
\end{array}
 \right) 
}
\end{equation}

Evidently the two matrices are related:
\begin{equation*}
C_h = N C_v N^T
\end{equation*}
where
	$N = \frac{1}{\sqrt{2}}
\left( 
\begin{array}{c c c}
 1 & 0		& 1\\
 1 & 0		& -1\\
 0 & \sqrt{2}	& 0
\end{array}
\right)$
